Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-09 thirdPaper/draft/typeConeAssociahedra.tex

\begin{example}
\label{exm:typeConeAsso}
Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$.
It has $3$ facet defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).

>>>>

\begin{example}
\label{exm:typeConeAsso}
Consider the fan~$\gvectorFan[2]$ and~$\gvectorFan[3]$ illustrated in \cref{fig:lodayFans}.
The type cone of~$\gvectorFan[2]$ lives in~$\R^5$ and has a linearity space of dimension~$2$ (this is the type cone studied in \cref{ex:typecone}).
It has $3$ facet-defining inequalities (given below), which correspond to the flips described in \cref{prop:extremalExchangeablePairsAsso} and illustrated in \cref{fig:labelFacetDefiningInequalititesAsso}\,(left).
